Highly Available Transactions: Virtues and Limitations

### 2013-04-01 writeup/evaluation.tex
fixed

This brief set of experiments is not meant as an exhaustive study, but
it validates our earlier intuition regarding the cost of violating
HAT-compliance. As Deutsch points out, ignoring factors such as
latency can ``cause big trouble and painful learning
experiences''~\cite{fallacies-deutsch}---in a single-site context,
paying the cost of coordination may be tenable, but, especially as
services are geo-replicated, the costs increase.

>>>>

This brief set of experiments is not meant as an exhaustive study, but
it validates our earlier intuition about the cost of violating
HAT-compliance. As Deutsch points out, ignoring factors such as
latency can ``cause big trouble and painful learning
experiences''~\cite{fallacies-deutsch}---in a single-site context,
paying the cost of coordination may be tenable, but, especially as
services are geo-replicated,  costs increase.
